To be FAIR: Theory Specification Needs an Update

### 2025-03-02 manuscript.Rmd
remove vertical dividers, closes #58

```{r figecs, eval = TRUE, fig.cap='Three implementations of the "empirical cycle" [@degrootMethodologieGrondslagenVan1961].'}
knitr::include_graphics("ec_visio.pdf")
```

>>>>

```{r figecs, eval = TRUE, fig.cap='Three implementations of the "empirical cycle" [@degrootMethodologieGrondslagenVan1961].'}
# rsvg::rsvg_pdf("empirical_cycle1.svg", "ec_visio.pdf")
knitr::include_graphics("ec_visio.pdf")
```
